Variants of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus

### 2016-11-07 Papers/InProgress/NaturalDeduction/GodProof-ND.tex
Fix typo

In every inference rule, (sub-)formulas in the conclusion correspond\footnote{This correspondence could be defined formally, but it would be tedious to do so.} to formulas in the premises (even in the case of quantifier rules, where the formulas differ due to substitution). For any expression occurring both in a formula in the premise and in its corresponding (sub-) formula in the conclusion, the occurrence in the premise is said to be an \emph{ancestor} of the occurrence in the conclusion, and the occurrence in the conclusion is said to be a \emph{descendant} of the occurrence in the premise.

@@

\bibitem[{\itshape Thiele(2003)}]{hilbert} Thiele, R. 2003. {\itshape Hilberts twenty-fourth problem}, American Mathematical Monthly, January 2003.

>>>>

In every inference rule, (sub-)formulas in the conclusion correspond\footnote{This correspondence could be defined formally, but it would be tedious to do so.} to formulas in the premises (even in the case of quantifier rules, where the formulas differ due to substitution). For any expression occurring both in a formula in the premise and in its corresponding (sub-)formula in the conclusion, the occurrence in the premise is said to be an \emph{ancestor} of the occurrence in the conclusion, and the occurrence in the conclusion is said to be a \emph{descendant} of the occurrence in the premise.

@@

\bibitem[{\itshape Thiele(2003)}]{hilbert} Thiele, R. 2003. {\itshape Hilbert's twenty-fourth problem}, American Mathematical Monthly, January 2003.
